Shaking out the idiosyncracies

### 2020-02-11 analysis/reports/vetting.Rmd
more relationships

@@

>>>>

```{r do fs chars predict perc, fig.dim = c(4,4)}
ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = simpson_range, y = simpson_percentile)) +
  geom_point(alpha = .1) +
  theme_bw()
ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = simpson_mean, y = simpson_percentile)) +
  geom_point(alpha = .05) +
  theme_bw()
ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = simpson_sd, y = simpson_percentile)) +
  geom_point(alpha = .1) +
  theme_bw()

ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = skew_range, y = skew_percentile)) +
  geom_point(alpha = .1) +
  theme_bw()
ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = skew_mean, y = skew_percentile)) +
  geom_point(alpha = .05) +
  theme_bw()
ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = skew_sd, y = skew_percentile)) +
  geom_point(alpha = .1) +
  theme_bw()
```

@@

```{r fs chars by dat, fig.dim = c(3,3)}
ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = dat, y = simpson_range)) +
  geom_boxplot() +
  theme_bw()
ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = dat, y = simpson_mean)) +
  geom_boxplot() +
  theme_bw()
ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = dat, y = simpson_sd)) +
  geom_boxplot() +
  theme_bw()
ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = dat, y = simpson_percentile)) +
  geom_boxplot() +
  theme_bw()
# Removing low n/s
ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE, log(n0/s0) >= 1.5), aes(x = dat, y = simpson_range)) +
  geom_boxplot() +
  theme_bw()
ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE, log(n0/s0) >= 1.5), aes(x = dat, y = simpson_mean)) +
  geom_boxplot() +
  theme_bw()
ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE, log(n0/s0) >= 1.5), aes(x = dat, y = simpson_sd)) +
  geom_boxplot() +
  theme_bw()
ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE, log(n0/s0) >= 1.5), aes(x = dat, y = simpson_percentile)) +
  geom_boxplot() +
  theme_bw()

ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = dat, y = skew_range)) +
  geom_boxplot() +
  theme_bw()
ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = dat, y = skew_mean)) +
  geom_boxplot() +
  theme_bw()
ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = dat, y = skew_sd)) +
  geom_boxplot() +
  theme_bw()
ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE), aes(x = dat, y = skew_percentile)) +
  geom_boxplot() +
  theme_bw()
# Removing low n/s
ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE, log(n0/s0) >= 1.5), aes(x = dat, y = skew_range)) +
  geom_boxplot() +
  theme_bw()
ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE, log(n0/s0) >= 1.5), aes(x = dat, y = skew_mean)) +
  geom_boxplot() +
  theme_bw()
ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE, log(n0/s0) >= 1.5), aes(x = dat, y = skew_sd)) +
  geom_boxplot() +
  theme_bw()
ggplot(data = filter(all_di, nsamples >= 2000, singletons == FALSE, log(n0/s0) >= 1.5), aes(x = dat, y = skew_percentile)) +
  geom_boxplot() +
  theme_bw()
```
